\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2022-02-02 slides/IASD/pres.tex
Update the survival model

\small
\begin{block}{Group-specific risk of event}
\begin{itemize}
  \item \footnotesize $\lambda(t|G = k) = \lambda_0(t) \exp \Big\{ \sum_{l=1}^L \sum_{a=1}^\cA {\gamma_{k,a}^l}^\top \varphi_{k, a}(t, b^l) \Big\}$
  \item Functionals $(\varphi_a)_{a\in \cA}$
\begin{table}[htb]
\centering
\resizebox{.9\textwidth}{!}{%
\begin{tabular}{ccccc}
\toprule
Description & $\varphi_{k,a}(t, b^l)$ & $\imath_a$ & Reference \\
\midrule
Linear predictor & $m_k^l(t)$ & 1 & \citet{chi2006joint} \\ [.15cm]
Random effects & $b^l$ & $r_l$ & \citet{hatfield2011joint} \\
Time-dependent slope & $\dfrac{\dd}{\dd t} m_k^l(t)$ & 1 & \citet{rizopoulos2011bayesian} \\ [.3cm]
Cumulative effect & $\int_0^t m_k^l(s) \dd s$ & 1 & \citet{andrinopoulou2017combined} \\ [.1cm]
 \bottomrule
\end{tabular}}
\end{table}

>>>>

\small
\begin{block}{Group-specific risk of event}
\begin{itemize}
  \item<1-> \footnotesize $\lambda(t|\Psi, G = k) = \lambda_0(t) \exp \big\{\gamma_k^\top \Psi \big\}$
  \item<2-> Fetures $\Psi$ are extracted from $Y$ by the \texttt{Python} library \texttt{tsfresh}
  \item<2-> \color{red}{TODO: Add descriptions}
